Simply Grasping Simple Shapes:\\ Commanding a Humanoid Hand with a Shape-Based Synergy

### 2017-10-11 draft_springer_2.tex
reworked the Current R2 Grasping section to de-emphasize AT and give a brief discription of the finger control

In practice, many humanoid systems will use some model based approach to manipulate objects encountered in the world. This can be seen through the DARPA Robotics Challenge (DRC) Trials in the ways the teams commanded their humanoids to interact with things like drills, door handles, valves, and other objects. \cite{DRC_Yanco}, \cite{IHMC}. Currently, the R2 project is using the Affordance Templates (AT) framework, initially presented in \cite{affordance_templates}. This system allows a model of an object to be created with different end effector waypoints to create allowable affordances for manipulating the object. Through this AT model, a catalog of different objects with their affordances is created and stored to be used throughout the manipulation process. However, in the current implementation, each new object encountered must have a new Affordance Template created before it can be manipulated. If generic models were available, any new object encountered that fit closely enough to an existing model could be used immediately, with no further development time.

@@

To create an Affordance Template, the user must first load in the mesh of the object to visualize in the simulated environment as well as give a collision model for motion planning. Next, the user must create different waypoints to dictate the necessary end-effector positions with respect to the object to give the affordance for a manipulation task. There can be multiple affordances per object, for example, a drill could be picked up via the handle or the top, making each approach its own affordance in the template. As part of each waypoint, the end-effector hand pose is dictated. R2`s current grasp library was constructed using the Cutosky Grasp Taxonomy \cite{Cutkosky} and these hand positions form the catalog of available hand poses. If a hand pose is required that is not in this catalog, the user must create a new pose via joint angle commands. The result of this template can be seen in Figure \ref{at_example}. This entire process can take multiple days per object to create and test.

It is readily apparent that this method of manipulation can be time consuming and very application specific. If the robot were to encounter an object slightly outside of the current template, a new template must be made. This will increase design, testing, and verification time to an intractable level for the deep space missions of the future. Instead, the design of single, generic models to be used for similar shapes based on object geometric synergies is proposed. For the cylinder synergies, the same AT framework can be implemented, using a cylindrical mesh corresponding to the diameter of the object. Then a standard set of approaches can be saved to approach the open side of the cylinder. Finally, the hand pose can be commanded based on the single DoF of diameter to close around the object. This would allow a flashlight, a coffee cup, a screwdriver, or any other cylinder to be picked up using the same template.

>>>>

R2's command structure centers around the concept of multi-loop control with a progressive series of loops \cite{r2_control}. The lowest level of control is a current loop, wrapped by a velocity loop, wrapped by a torque loop, and finally wrapped by a position loop that the user is dictating. However, the R2 finger actuators are not series elastic and have no direct torque measurement. Therefore, the torque loop is removed in the multi-loop control model and current limiting is placed at the lowest level to protect the finger tendons. This loop structure eliminates the capability to do direct torque control of the fingers to close around an object. This dictates the need for a position control scheme to command the hand to manipulate objects.

@@

Due to this position control scheme, the original grasp process used by R2 was based on the Cutkosky Grasp Taxonomy \cite{Cutkosky}. This series of 24 position defined grasps composed the main method of manipulating an object in conjunction with the Affordance Template Framework \cite{affordance_templates} similar to systems used on other humanoid robots \cite{DRC_Yanco}, \cite{IHMC}. However, each of these templates, an example of which is shown in Fig \ref{at_example}, is unique to the object using one of the Cutcosky grasps. If a new grasp is needed, it must be created, tested and verified. If a new object that is slightly different than a current known object is encountered, a new Affordance Template and grasp must be created and tested.

This creation of templates and gasp positoins can be time consuming and very application specific and is intractable at a large scale for robots in practice. In addition, the current proposed methods of using the synergies based on the PCA of the human hand are equally non-intuitve to program in a position based scheme. Therefore, a commanding structure to determine hand position based on simple properties of the object is proposed. Specifically for this work, the authors propose a geometric synergy based on cylindrical type objects. The finger position can be commanded based on the single DoF dictated by the diamter of the object. This would allow a flashlight, a coffee cup, a screwdrirver, and any other cylinder to be manipulated using the same cylindrical template based solely on the objects diameter.
